Reparametrization of COM-Poisson Regression Models with Applications in the Analysis of Experimental Data

### 2017-10-31 article.Rnw
Modify the size, align and position of tables

library(knitr)
library(xtable)
options(digits = 3, OutDec = ".",
        xtable.caption.placement = "top",
        xtable.booktabs = TRUE,
        xtable.sanitize.text.function = identity)
opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    echo = FALSE,
    results = "hide",
    fig.width = 7,
    fig.height = 5,
    out.width = "1\\textwidth",
    fig.align = "center",
    fig.pos = "H",
    # dev = "tikz"
    dev.args = list(family = "Palatino")
    )

@@

\begin{document}
\maketitle

@@

\begin{table}[h]
\centering
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the cotton
  experiment.}
\label{tab:coef-cotton}
\begin{tabularx}{\textwidth}{lCCCCCCCC}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<results-cotton, results="asis">>=

@@

# Organize in table
pnames <- c("\\phi\\,,\\,\\sigma", "\\beta_0",
            paste0("\\beta_{1", 1:5, "}"),
            paste0("\\beta_{2", 1:5, "}"))
rownames(est.ncap) <- paste0("$", pnames, "$")
meds <- apply(do.call(cbind, measures.ncap), 1, function(x) {
    x <- formatC(x, getOption("digits"), format = "f")
    x <- gsub("NA", "---", x)
    paste(paste0("\\multicolumn{2}{c}{", x, "}"),
          collapse = " & ")
})
text_gof <- paste(paste(names(meds), "&", meds),
                  collapse = "\\\\\n ")

@@

<<desc-soy, fig.pos="H", fig.height=4, fig.width=8, fig.cap="Number of grains per pot for each potassium dose and moisture level (left) and sample mean agains sample variance of the five replicates for each experimental treatment (right).">>=

@@

\begin{table}[ht]
\centering
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the soybean
  experiment.}
\label{tab:coef-soy}
\begin{tabularx}{\textwidth}{lCCCCCCCC}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<results-soya, results="asis">>=

@@

rownames(est.ngra) <- paste0("$", pnames, "$")
meds <- apply(do.call(cbind, measures.ngra), 1, function(x) {
    x <- formatC(x, getOption("digits"), format = "f")
    x <- gsub("NA", "---", x)
    paste(paste0("\\multicolumn{2}{c}{", x, "}"),
          collapse = " & ")
})
text_gof <- paste(paste(names(meds), "&", meds),
                  collapse = "\\\\\n ")

@@

<<pred-soy, fig.pos="H", fig.height=3.8, fig.width=8, fig.cap="Dispersion diagrams of grain counts as function of potassium doses and humidity levels with fitted curves and confidence intervals (95\\%).">>=

@@

\begin{table}[ht]
\centering
\caption{Model fit measures and comparisons between predictors and models.}
\label{tab:anova-ovos}
\begin{tabularx}{\textwidth}{lCCCCCrC}
  \toprule
 Poisson & np & $\ell$ & AIC & 2(diff $\ell$) & diff np & P($>\rchi^2$) & \\
 \midrule
<<anova-ovos1, results="asis">>=

@@

\begin{table}[H]
\centering
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the nitrofen
  experiment.}
\label{tab:coef-ovos}
\begin{tabularx}{\textwidth}{lCCCCCCCC}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<coef-ovos, results="asis">>=

@@

%-----------------------------------------------------------------------
\newpage

\small
\bibliography{references.bib}
\end{document}

>>>>

library(knitr)
library(xtable)
options(digits = 3, OutDec = ".",
        xtable.caption.placement = "top",
        xtable.booktabs = TRUE,
        xtable.sanitize.text.function = identity,
        xtable.size = "small",
        xtable.math.style.negative = TRUE)
opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    echo = FALSE,
    results = "hide",
    fig.width = 7,
    fig.height = 5,
    out.width = "1\\textwidth",
    fig.align = "center",
    fig.pos = "!ht",
    # dev = "tikz"
    dev.args = list(family = "Palatino")
    )

@@

\begin{document}

\maketitle

@@

\begin{table}[!ht]
\centering \small
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the cotton
  experiment.}
\label{tab:coef-cotton}
\begin{tabularx}{\textwidth}{lrrrrrrrr}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<results-cotton, results="asis">>=

@@

# Organize in table
pnames <- c("\\phi\\,,\\,\\sigma", "\\beta_0",
            paste0("\\beta_{1", 1:5, "}"),
            paste0("\\beta_{2", 1:5, "}"))
rownames(est.ncap) <- paste0("$", pnames, "$")
meds <- apply(do.call(cbind, measures.ncap), 1, function(x) {
    x <- formatC(x, getOption("digits"), format = "f")
    x <- gsub("NA", "-", x)
    paste(paste0("\\multicolumn{2}{c}{$", x, "$}"),
          collapse = " & ")
})
text_gof <- paste(paste(names(meds), "&", meds),
                  collapse = "\\\\\n ")

@@

<<desc-soy, fig.pos="!ht", fig.height=4, fig.width=8, fig.cap="Number of grains per pot for each potassium dose and moisture level (left) and sample mean agains sample variance of the five replicates for each experimental treatment (right).">>=

@@

\begin{table}[!ht]
\centering \small
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the soybean
  experiment.}
\label{tab:coef-soy}
\begin{tabularx}{\textwidth}{lrrrrrrrr}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<results-soya, results="asis">>=

@@

rownames(est.ngra) <- paste0("$", pnames, "$")
meds <- apply(do.call(cbind, measures.ngra), 1, function(x) {
    x <- formatC(x, getOption("digits"), format = "f")
    x <- gsub("NA", "-", x)
    paste(paste0("\\multicolumn{2}{c}{$", x, "$}"),
          collapse = " & ")
})
text_gof <- paste(paste(names(meds), "&", meds),
                  collapse = "\\\\\n ")

@@

<<pred-soy, fig.pos="!ht", fig.height=3.8, fig.width=8, fig.cap="Dispersion diagrams of grain counts as function of potassium doses and humidity levels with fitted curves and confidence intervals (95\\%).">>=

@@

\begin{table}[!ht]
\centering \small
\caption{Model fit measures and comparisons between predictors and models.}
\label{tab:anova-ovos}
\begin{tabularx}{\textwidth}{lcccccrc}
  \toprule
 Poisson & np & $\ell$ & AIC & 2(diff $\ell$) & diff np & P($>\rchi^2$) & \\
 \midrule
<<anova-ovos1, results="asis">>=

@@

\begin{table}[!ht]
\centering
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the nitrofen
  experiment.}
\label{tab:coef-ovos}
\begin{tabularx}{\textwidth}{lCCCCCCCC}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<coef-ovos, results="asis">>=

@@

%-----------------------------------------------------------------------
\bibliography{references.bib}

\end{document}
